### 2016-02-07 ch06-concl/conclusions.tex
initvals almost finished

  On the other hand, the \gls{LRM} and its variants discussed in \chapref{sec:nonparametric} provide some local information regarding the shape of the \gls{FRF} and hence also the transfer function.
  The usefulness has already been seen in \chapref{sec:hinf} in connection to the computation of the \Hinf norm of a system.
  Intrinsically, these local rational methods approximate the transfer function by a local model, or, equivalently a set of local poles and zeros.
  Especially for resonant poles, one can expect that these local poles are closely linked to the global (actual) poles of a system.
  As such, those could provide a valuable initialization strategy if the redundant local pole/zero information of neighboring windows can be reduced to a single global pole/zero initial value.
  \TODO{optimal smoother}

>>>>

  On the other hand, the \gls{LRM} and its variants discussed in \chapref{sec:nonparametric} provide some local information regarding the shape of the \gls{FRF} and hence also the transfer function.
  The usefulness has already been illustrated in \chapref{sec:hinf} in connection to the computation of the \Hinf norm of a system.
  Intrinsically, these local rational methods approximate the transfer function by a local model, or, equivalently a set of local poles and zeros.
  Especially for resonant poles, one can expect that these local poles are closely linked to the global (physical) poles of a system.
  As such, those could provide a valuable initialization strategy if the redundant local pole/zero information of neighboring windows can be reduced to a single global pole/zero initial value.
  Probably techniques in model order reduction could provide a good starting point to calculate such initial values.
  \TODO{optimal smoother}
